### 2022-01-07 src-latex/parts/60-results.tex
Proposition d'intro: à corriger/compléter/amender...
Début d'état de l'art: à finir aujourd'hui.

\subsection{Experiment 2: Accuracy vs NER approach vs OCR noise}

>>>>

\subsection{Experiment 2: sensibility to training on noisy data}
Idea : Measure the impact of training with noisy data when predicting NER tags on both clean and noisy data.

What's interesting : do models perform better on noisy data when trained on noisy data ? Does it impact predictions on clean data ?

Table : NER NN models VS train on {noisy, clean} datasets VS evaluate on {noisy, clean} datasets

\subsection{Experiment 3: Accuracy vs NER approach vs OCR noise}
